---
title: "simpleRegress"
author: "Jovygomez"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared is 0.7476


## Model LENGTH ~ AGE  this is an example  

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared is 0.5073

## Model LENGTH ~ HEADLEN this is an example  

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted R-squared is 0.8434

## Model LENGTH ~ HEADWTH this is an example  

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted R-squared is 0.5321

## Model LENGTH ~ CHEST  this is an example  

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted R-squared is 0.7869

## Model LENGTH ~ WEIGHT  this is an example  

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```
The adjusted R-squared is 0.7423

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

Comparing all of the models that predict LENGTH other than Neck. Ranking (from worst to best):

AGE (Adjusted R² = 0.5073). 
HEADWTH (Adjusted R² = 0.5321). 
WEIGHT(Adjusted R² = 0.7423).  
CHEST (Adjusted R² = 0.7869).  
HEADLEN (Adjusted R² = 0.8434). 

